\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize COMM XXX: Social Data APIs and Analysis -- Summer 2022}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={COMM XXX: Social Data APIs and Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}





\usepackage{setspace}

\title{COMM XXX: Social Data APIs and Analysis}
\author{Ross Dahlke}
\date{Summer 2022}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}


	\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:rdahlke@stanford.edu}{\nolinkurl{rdahlke@stanford.edu}}} & Web: TBD\\
Office Hours: TBD  &  Class Hours: TBD\\
Office: TBD  & Class Room: TBD\\
	&  \\
	\hline
	\end{tabular*}
	
\vspace{2mm}
	


\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

This class will combine theoretical and technical discussions and labs
to give students the ability to conduct their own research with digital
social data. Every week we will have discussions on the structure,
content, and userbase of various social platforms and what that means
for the data that is generated from them. We will also learn how to
access data from these platforms via their web APIs or other databases
in addition to how to analyze these data. Finally, students will be able
to answer their own unique research questions. By the end of the course,
students should be well positioned to conduct their own original
research.

\textbf{Students should have a working understanding of the statistical
programming language R}. This class is not an introductory computing
course. We will be covering how to access web APIs and analyze the data
from these sources, but students are expected to already know basics of
computing such as data types, data cleaning, and basic analysis.

In addition, this course will primarily be using the \texttt{tidyverse}
for programming. If you are unfamiliar with the \texttt{tidyverse}
please review Hadley Wickham's \href{https://r4ds.had.co.nz/}{R for Data
Science}, which can be found for free online.

This course will be primarily taught using R. Students are highly
encouraged to use R. It is my opinion that R is the best choice for
individuals who wish to conduct computational social science research or
pursue data science in industry. However, students are able to use
Python but must be aware that they will be responsible for finding the
necessary resources in Python to complete their assignments and project
on their own.

\hypertarget{course-objectives}{%
\section{Course Objectives}\label{course-objectives}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Better understand the uniqueness of digital social platforms
\item
  Know how to access social data via web APIs
\item
  Learn how to analyze social data retrieved from the web
\item
  Conduct and present original research
\end{enumerate}

\hypertarget{required-readings}{%
\subsection{Required Readings}\label{required-readings}}

There will not be any books that need to be bought for this course.
Instead, students will have assigned readings each week. Please read
through the technical documentation and examples of academic research
for each week prior to the first class of the week.

\hypertarget{grading-policy}{%
\subsection{Grading Policy}\label{grading-policy}}

\begin{itemize}
\item
  \textbf{20\%} of your grade will come from Platform Reviews
\item
  \textbf{30\%} of your grade will come from the weekly lab assignments
\item
  \textbf{10\%} of your grade will come from your project proposal
\item
  \textbf{10\%} of your grade will come from your project presentation
\item
  \textbf{20\%} of your grade will come from your project paper
\end{itemize}

\hypertarget{attendance-policy}{%
\subsection{Attendance Policy}\label{attendance-policy}}

Attendance is not mandatory for this course. However, Platform Reviews
will only be accepted at the beginning of class on Mondays. The labs are
intended to give students enough time to to complete most, if not all,
of the lab assignment in lab. During lab you will have access to the
instructor for questions, and you are encouraged to work with other
students during the labs.

\hypertarget{e-mail-policy}{%
\subsection{E-mail Policy}\label{e-mail-policy}}

Students can expect an response within 24 hours during the week. Please
start the subject line of your email with ``COMM XXX: {[}your name{]}''.

\hypertarget{academic-dishonesty-policy}{%
\subsection{Academic Dishonesty
Policy}\label{academic-dishonesty-policy}}

Students are expected to abide by the Stanford Honor Code
(\url{https://communitystandards.stanford.edu/student-conduct-process/honor-code-and-fundamental-standard})
.

\hypertarget{accessibility}{%
\subsection{Accessibility}\label{accessibility}}

Students in need of accommodation due to a disability should file a
request with the Office of Accessible Education (OAE). OAE will prepare
an Accommodation letter for the instructor. OAE is located at 563
Salvatierra Walk. \url{https://oae.stanford.edu/}

\newpage

\hypertarget{class-schedule}{%
\section{Class Schedule}\label{class-schedule}}

\hypertarget{week-1-introduction}{%
\subsection{Week 1: Introduction}\label{week-1-introduction}}

\begin{itemize}
\tightlist
\item
  About this course
\item
  R \& RStudio
\item
  Rmarkdown
\end{itemize}

\hypertarget{week-2-twitter}{%
\subsection{Week 2: Twitter}\label{week-2-twitter}}

Technical documentation

\begin{itemize}
\tightlist
\item
  \texttt{rtweet} \url{https://github.com/ropensci/rtweet}
\item
  Twitter API \url{https://developer.twitter.com/en/docs}
\end{itemize}

Examples of research

\begin{itemize}
\tightlist
\item
  Barberá P, Rivero G. Understanding the Political Representativeness of
  Twitter Users. \emph{Social Science Computer Review}.
  2015;33(6):712-729. \url{doi:10.1177/0894439314558836}
\item
  Barberá, P. (2015). Birds of the Same Feather Tweet Together: Bayesian
  Ideal Point Estimation Using Twitter Data. \emph{Political Analysis},
  23(1), 76-91. \url{doi:10.1093/pan/mpu011}
\end{itemize}

\hypertarget{week-3-tik-tok}{%
\subsection{Week 3: Tik tok}\label{week-3-tik-tok}}

Technical documentation

\begin{itemize}
\tightlist
\item
  \texttt{tiktokr} \url{https://github.com/benjaminguinaudeau/tiktokr}
\item
  pushshift.io Tik Tok data \url{https://files.pushshift.io/tiktok/}
\end{itemize}

Examples of research

\begin{itemize}
\tightlist
\item
  Zhu, C.; Xu, X.; Zhang, W.; Chen, J.; Evans, R. How Health
  Communication via Tik Tok Makes a Difference: A Content Analysis of
  Tik Tok Accounts Run by Chinese Provincial Health Committees.
  \emph{Int. J. Environ. Res. Public Health} 2020, 17, 192.
  \url{https://www.mdpi.com/1660-4601/17/1/192\#cite}
\item
  Moran, P. Social Media: A Pandemic of Misinformation. \emph{The
  American Journal of Medicine} 2020, 133, 11.
  \url{https://www.amjmed.com/article/S0002-9343(20)30519-2/abstract}
\end{itemize}

\hypertarget{week-4-reddit}{%
\subsection{Week 4: Reddit}\label{week-4-reddit}}

Technical documentation

\begin{itemize}
\tightlist
\item
  \texttt{RedditExtractoR}
  \url{https://github.com/ivan-rivera/RedditExtractoR}
\item
  Reddit API \url{https://www.reddit.com/dev/api/}
\item
  Baumgartner, J., Zannettou, S., Keegan, B., Squire, M., \& Blackburn,
  J. (2020). The Pushshift Reddit Dataset. \emph{Proceedings of the
  International AAAI Conference on Web and Social Media}, 14(1),
  830-839. Retrieved from
  \url{https://ojs.aaai.org/index.php/ICWSM/article/view/7347}
\end{itemize}

Examples of research

\begin{itemize}
\tightlist
\item
  Shen, J. D.; Rudzic, F. Detecting anxiety on Reddit. \emph{Proceedings
  of the Fourth Workshop on Computational Linguistics and Clinical
  Psychology} 2017. The Association for Computational Linguistics.
  \url{https://www.aclweb.org/anthology/W17-3107.pdf}
\item
  Cody Buntain and Jennifer Golbeck. 2014. Identifying social roles in
  reddit using network structure. \emph{In Proceedings of the 23rd
  International Conference on World Wide Web (WWW '14 Companion)}.
  Association for Computing Machinery, New York, NY, USA, 615--620.
  \url{DOI:https://doi.org/10.1145/2567948.2579231}
\end{itemize}

\hypertarget{week-5-youtube}{%
\subsection{Week 5: YouTube}\label{week-5-youtube}}

Technical documentation

\begin{itemize}
\tightlist
\item
  \texttt{tuber} \url{https://github.com/soodoku/tuber}
\item
  YouTube API \url{https://developers.google.com/youtube/v3}
\end{itemize}

Examples of research

\begin{itemize}
\tightlist
\item
  Wattenhofer, Mirjam; Wattenhofer, R.; Zhu, Z. The YouTube Social
  Network. 2012. \emph{In Sixth International AAAI Conference on Weblogs
  and Social MEdia (ICWSM 2012)}.
  \url{https://research.google/pubs/pub37738/}
\item
  X. Cheng, C. Dale and J. Liu, ``Statistics and Social Network of
  YouTube Videos,'' 2008 \emph{16th Interntional Workshop on Quality of
  Service,} Enschede, 2008, pp.~229-238, doi: 10.1109/IWQOS.2008.32.
\end{itemize}

\hypertarget{week-6-news}{%
\subsection{Week 6: News}\label{week-6-news}}

Technical documentation

\begin{itemize}
\tightlist
\item
  \texttt{newsAPI} \url{https://github.com/mkearney/newsAPI}
\item
  News API \url{https://newsapi.org/}
\end{itemize}

Examples of research

\begin{itemize}
\tightlist
\item
  Lei Guo \& Yiyan Zhang (2020) Information Flow Within and Across
  Online Media Platforms: An Agenda-setting Analysis of Rumor Diffusion
  on News Websites, Weibo, and WeChat in China, \emph{Journalism
  Studies}, 21:15, 2176-2195, DOI: 10.1080/1461670X.2020.1827012
\item
  S. Mo Jang, Brooke W. Mckeever, Robert Mckeever \& Joon Kyoung Kim
  (2019) From Social Media to Mainstream News: The Information Flow of
  the Vaccine-Autism Controversy in the US, Canada, and the UK,
  \emph{Health Communication}, 34:1, 110-117, DOI:
  10.1080/10410236.2017.1384433
\item
  Matthew S. Weber, Peter Monge, The Flow of Digital News in a Network
  of Sources, Authorities, and Hubs, \emph{Journal of Communication},
  Volume 61, Issue 6, December 2011, Pages 1062--1081,
  \url{https://doi.org/10.1111/j.1460-2466.2011.01596.x}
\end{itemize}

\hypertarget{week-7-project-meetings-worktime}{%
\subsection{Week 7: Project Meetings \&
Worktime}\label{week-7-project-meetings-worktime}}

Meet with course instructor

\hypertarget{week-8-presentations}{%
\subsection{Week 8: Presentations}\label{week-8-presentations}}




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
